---
title: "Your Turn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rio)
```

# Your Turn 1

1. Import the file `pragmatic_scales_data.csv` (use best practices of a project-oriented workflow). Save it to an object called `ps_data`. This time we'll save it as a `tibble` (which I've done for you).

```{r}
# Q1. 
 
ps_data <- import(___) %>% 
  as_tibble()
```


2. Filter rows for cases in the "No Label" `condition` and arrange the resulting observations by descending order of `age`.

```{r}
#Q2. 

ps_data %>% 
  filter(___) %>% 
  arrange(___)
```


3. Select observations from the “No Label” condition for kids 3 years old or younger. 

```{r}
# Q3. 

ps_data %>% 
  filter(___)
```


4. Select observations for kids between the ages of 3 and 4. (Extra challenge: look up the documentation for `between()` and use this function.)

```{r}
# Q4. 

___ <- ps_data %>% 
  filter(___)
```



# Your Turn 2


1. In `ps_data`, select only the variables `age` and `condition`. 

```{r}
# Q1.

ps_data %>% 
  select(___)
```


2. As we did with indexing in base R, you can use the minus sign (`-`) to "de-select" columns. Keep everything in `ps_data` except `subid` and `condition`. 

```{r}
# Q2.

ps_data %>% 
  select(___)
```


3. Select the columns `correct` and `condition` without naming them, using their positions or de-selecting other variables.

```{r}
# Q3. 

ps_data %>% 
  select(___)
```


4. Use `mutate()` to convert `condition` from type "character" to type "factor". Hint: what function could you pipe to directly to check this? 

```{r}
#Q4. 

ps_data %>% 
  mutate(___) %>% 
  ___
```



# Your Turn 3

1. From `ps_data`, get the total number of correct trials for each subject and call this variable `num_correct`. Hint: you can use the summary function `sum()`. 

```{r}
# Q1. 

ps_data %>% 
  group_by(___) %>% 
  summarize(___ = sum(___))
```


2. Now get the total number of correct trials (`num_trials`) for each unique combination of `condition` and `item` and arrange the resulting rows by descending order of `num_correct`. Which combination of condition and item had the most/least correct responses? 

```{r}
# Q2. 

ps_data %>% 
  group_by(___, ___) %>% 
  summarize(___ = sum(___)) %>% 
  arrange(desc(___))
```


3. Lastly, calculate the proportion of correct responses for each `condition` and call this variable `prop_correct` (hint: because `correct` is coded as 0 and 1, you can do this by taking the mean of `correct`). In the same pipeline, create a bar plot that shows the differences between the mean proportion of correct responses between the two conditions, and color the bars by condition.

```{r}
# Q3. 

ps_data %>% 
  group_by(___) %>% 
  summarize(prop_correct = mean()) %>% 
  ggplot(___(x = ___, y = ___, fill = ___)) + 
  ___() +
  coord_flip() # don't need to change this
```


```{r}
ps_data %>% 
    group_by(condition) %>% 
    summarize(prop_correct = mean(correct)) %>% 
    ggplot(aes(x = prop_correct, y = condition, fill = condition)) + 
    geom_col() + 
    coord_flip() + 
    theme_bw() + 
  labs(x = "Condition", y = "Proportion Correct")
```

