---
title: "Basics of R & RStudio"
author: 
date: 
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css, "assets/css/custom.css"]
    seal: false
    lib_dir: libs
  nature:
    highlightStyle: github
    highlightLines: true
    countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(countdown)
library(tidyverse)

xaringanExtra::use_xaringan_extra(include = c("panelset", "tile_view", "share_again"))
xaringanExtra::style_share_again(share_buttons = c("twitter", "linkedin", "pocket"))
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(base_color = "#23395b",
                text_font_google = google_font("Montserrat", "300", "300i"),
                code_font_google = google_font("Source Code Pro"),
                link_color = "#5e8c61")
```

class: title-slide, center, middle

# Basics of R & RStudio

---
# Learning objectives 

---
# Getting comfortable with RStudio

Let's start by looking at how RStudio is organized

--
<br><br><br>

.center[
### ~Launch RStudio Cloud~
# [`r fontawesome::fa("r-project", height = "150px")`](https://bit.ly/3caJRCN)
]

---
# Basic computing

```{r}
# Addition
2 + 3

# Subtraction
2 - 3

# Multiplication
2 * 3

# Division
10/2
```


---
# Basic computing

```{r}
# Exponents
4^2

# Roots
4^(1/2)
```

--

+ Thankfully, R follows the order of operations (PEMDAS).

```{r}
2^3 + 4 * 1/2
```

--

+ These values aren’t stored anywhere though...

---
# Storing values in objects

+ To keep a value in memory, we need to assign it to an **object**. 

--

+ To assign a value to an object, use the **assignment operator**. It looks like a left-pointing arrow: 

.center[
#`<-`
]

--

+ Let's use `<-` to create an object called x, that is assigned the number 8. 

```{r}
x <- 8 
```

--

+ Now we can call `x` by name; if we do this, it will print the value.

```{r}
x
```

---
# Style

+ Technically, both `<-` and `=` both work as assignment operators. But we'll strictly use `<-` from here on out. This brings up a general coding principle of the day...

--

+ *Style is important!* You want to use a consistent style so that others (including your future self) can easily and quickly read your code. 

  + I highly recommend following the [tidyverse style guide](https://style.tidyverse.org/). 

--

+ Hint: You will type `<-` a LOT. The keyboard shortcut `Alt+-` or `Option+-` can be used to insert a `<-`.

---
# Storing values in objects

+ Now, let's take a look at the variable `y`

--

```{r error=TRUE}
# call y
y 
```

+ Whoops! We didn't assign anything to `y`. Calling a variable that doesn't exist leads to an **error message**. 

+ You'll see a LOT of error messages when using R. This is *100% normal*. Don't worry when this happens. 

--

```{r}
# Need to assign something to y!
y <- 2

y
```

---
