---
title: "Data Types & Structures"
author: 
date: 
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css, "assets/css/custom.css"]
    seal: false
    lib_dir: libs
  nature:
    highlightStyle: github
    highlightLines: true
    countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(countdown)
library(tidyverse)

xaringanExtra::use_xaringan_extra(include = c("panelset", "tile_view", "share_again"))
xaringanExtra::style_share_again(share_buttons = c("twitter", "linkedin", "pocket"))

# your turn counter
yt_counter <- 0
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#23395b",
                text_font_google = google_font("Montserrat", "300", "300i"),
                code_font_google = google_font("Source Code Pro"),
                link_color = "#BA8800",
                code_inline_color = "#BA8800")
```

class: title-slide, center, middle

# Data Types & Structures

---
# Types of data

+ R has different types of data, and an object’s type affects how it interacts with functions and other objects. 

--

+ So far, we’ve just been working with integers. R has several other types of data

--

Type | Definition | Example
-----|------------|--------
Integer | whole numbers from -Inf to +Inf | 1, 2, -1, -10928
Numeric / Double | fractions & decimals from -Inf to +Inf | 1.3, .293764, -.1239217, `Inf`, `-Inf`
Character / String | quoted strings of letters, numbers, and allowed symbols| "1", "one", "o_n_e", "o-n-e", "o.n.e"
Logical / Boolean | logical constants of True or False | `TRUE`, `FALSE`, `T`, `F`
factor | ordered, labelled variable | variable for year in college labelled "Freshman", "Sophomore", etc.

---
# Types of data 

+ There are a few special types worth knowing about too:

Type | Definition |Example
-----|------------|-------
NA   | Missing value; technically represented as different types but displayed as `NA` | `NA`, `NA_character_`, `NA_integer_`
NaN  | Not a Number | 0/0
+Inf | Positive infinity | `Inf`
-Inf | Negative infinity | `-Inf`
NULL | The `NULL` object; an object that exists but is completely empty | `NULL`

---
# Types of data 

+ You can use `typeof()` to find out the type of a value or object:

```{r}
typeof(1)
typeof(TRUE)
typeof(1L)
typeof("one")
```

---
# Types of data 

```{r}
typeof(NA)
typeof(NA_character_)
typeof(NULL)
typeof(Inf)
```

---
class: inverse, center, middle
# Data structures 

---
# Vectors 

+ Often, we’re not working with individual values, but with multiple related values or a **vector** of values.

--
***

+ We can create a vector of ordered numbers using `starting_number`:`ending_number`. For example, we could make `x` a vector with the numbers between 1 and 5.

```{r}
x <- 1:5
x
```

--
***
+ Let's look at the Environment pane in RStudio... `r icon::fa("cloud")` 

Since `x` is a vector, it tells us what type of vector it is and it's length in addition to its contents (which can be abbreviated if the object is larger).

---
# Vectors

We can create a vector of any numbers we want using `c()`, which is a **function**. You can think of `c()` as short for "combine".

You use `c()` by putting numbers seperated by a comma (`,`) within the parentheses.

```{r}
x <- c(2, 8.5, 1, 9)
x
```


--
***

We can also create a vector of numbers using `seq()`. 

`seq()` is a function that creates a sequence of numbers. To learn how any R function works, you can access the help documentation by typing <br> `?+function_name`. 

--
***

Let's take a look at how `seq()` works... `r icon::fa("cloud")` 

```{r eval=FALSE}
?seq
```


---
# Vectors 

What happens if we run `seq()` with no arguments?

```{r}
seq()
```

--
***

.panelset[

.panel[.panel-name[Question]
Why did this happen?
]

.panel[.panel-name[Answer]

The `seq()` function has **arguments** with default values. 

The first two arguments are `from = ` and `to = `, which specify the starting and end values of the sequence. By *default* `from = 1` and `to = 1`. 

This means that typing `seq()` is equivalent to typing `seq(from = 1, to = 1)`, which generates a sequence with just one value: `1`.

We will talk more about how functions work in the next slide deck!
]
]

--
***

To make a sequence from 1 to 5 with this function, we have to set the `from =` and `to =` to those boundaries:

```{r}
seq(from = 1, to = 5)
```

---
# Vectors

We can also set one or more of the other arguments. The `by = ` argument allows us to change the increment of the sequence. Let's say we wanted every other number between 1 and 5. We can do this by setting `by = 2`

```{r}
seq(from = 1, to = 5, by = 2)
```

---
# Vectors

Vectors are just 1-dimensional sequences **of a single type of data**.

Note that vectors can also include strings or character values.

```{r}
letters <- c("a", "b", "c", "d")
letters
```

--
***

The general rule R uses is to set the vector to be the most "permissive" type necessary. 

For example, what happens if we put the vectors `x` and `letters` together?

```{r}
mixed_vec <- c(x, letters)
mixed_vec
```

---
# Vectors

```{r}
mixed_vec
```

Notice the quotes? R turned all of our numbers into strings, since strings are more "permissive" than numbers. 

--


```{r}
typeof(mixed_vec)
```

--
***

This is called **coercion**. R coerces a vector into whichever type will accomodate all of the values. We can coerce `mixed_vec` to be numeric using `as.numeric()`

```{r}
as.numeric(mixed_vec)
```

---
class: inverse
# Your turn `r (yt_counter <- yt_counter + 1)`

```{r echo=FALSE}
countdown(minutes = 1, seconds = 30)
```

Create an object called `x` that is assigned the number 8. 

Create an object called `y` that is a sequence of numbers from 2 to 16, by 2. 

Add `x` and `y`. What happens? 

---
class: solution

# Solution

```{r}
x <- 8

y <- seq(from = 2, to = 16, by = 2)

x + y
```

---
class: inverse
# Your turn `r (yt_counter <- yt_counter + 1)`

```{r echo=FALSE}
countdown(minutes = 1, seconds = 30)
```


1. Create an object called `a` that is just the letter "a" and an object `x` that is assigned the number 8. Add `a` to `x`. What happens?

2. Create a vector called `b` that is just the number 8 in quotes. Add `b` to `x` (from above). What happens?

3. Find some way to add `b` to `x`. (*Hint*: Don't forget about coercion.)

---
class: solution 
# Solution


```{r error=TRUE}
# 1.
a <- "a"
x <- 8

a + x 
```

```{r error=TRUE}
# 2.
b <- "8"

b + x
```

```{r}
# 3.
as.numeric(b) + x
```

---
# Indexing vectors

### Indexing by position

The last thing to mention about vectors is that they are all indexed numerically in R, starting with 1. Since vectors are only 1 dimension, we index them with a single number in `[]`. 

--
***

Let's take a new vector `z` as an example:

```{r}
z <- 6:10
```

--
***

.panelset[
.panel[.panel-name[Example 1]

Let's get just the first element of `z`:

```{r}
z[1]
```

]

.panel[.panel-name[Example 2]

Get the first and third element by passing those indexes as a vector using `c()`.

```{r}
z[c(1, 3)]
```
]
]

---
# Indexing Vectors

### Negative indexing

We could also say which elements *not* to give us using the minus sign (`-`). 

--
***

```{r}
z <- 6:10
```

.panelset[
.panel[.panel-name[Example 1]

Let's get rid of the first element:

```{r}
z[-1]
```
]

.panel[.panel-name[Example 2]

Get rid of the first and third elements

```{r}
z[-c(1, 3)]
```
]
]

---
# Indexing Vectors 

### Indexing by name

Finally, if the elements in the vector have names, we can refer to them by name instead of their numerical index. You can see the names of a vector using `names()`.

```{r}
names(z)
```

--
***

Looks like the elements in `z` have no names.  We can change that by assigning them names using a vector of character strings.

```{r}
names(z) <- c("first", "second", "third", "fourth", "fifth")
z
```

---
# Indexing Vectors 

### Indexing by name

```{r}
z
```

--
***

Now we can use the names of the elements in `z` for subsetting. 

```{r}
z["first"]
```

---
# Indexing Vectors 

### Manipulating elements in vectors

One thing that you can do with indexing is change elements within the vector. 

--
***

.panelset[
.panel[.panel-name[Example 1]

We could change the first element of `z` to missing, or `NA`.

```{r}
z[1] <- NA
z
```
]

.panel[.panel-name[Example 2]

You can also use indexing to transform a single element in a vector. Let's raise the second element of `z` to the power of 2.

```{r}
z[2] <- z[2]^2
z
```
]

.panel[.panel-name[Example 3]

Or use it to add to a vector. Let's add the number 11 as the sixth element of the vector `z`.

```{r}
z[6] <- 11
z
```
]

.panel[.panel-name[Example 4]
And you can add a name for that element by referencing the index for the `names` attribute of `z`.

```{r}
names(z)[6] <- "sixth"
z
```
]
]

---

