---
title: "Data Types & Structures"
author: 
date: 
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css, "assets/css/custom.css"]
    seal: false
    lib_dir: libs
  nature:
    highlightStyle: github
    highlightLines: true
    countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(countdown)
library(tidyverse)

xaringanExtra::use_xaringan_extra(include = c("panelset", "tile_view", "share_again"))
xaringanExtra::style_share_again(share_buttons = c("twitter", "linkedin", "pocket"))

# your turn counter
yt_counter <- 0
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#23395b",
                text_font_google = google_font("Montserrat", "300", "300i"),
                code_font_google = google_font("Source Code Pro"),
                link_color = "#BA8800",
                code_inline_color = "#BA8800")
```

class: title-slide, center, middle

# Data Types & Structures

---
# Types of data

+ R has different types of data, and an object’s type affects how it interacts with functions and other objects. 

--

+ So far, we’ve just been working with integers. R has several other types of data

--

Type | Definition | Example
-----|------------|--------
Integer | whole numbers from -Inf to +Inf | 1, 2, -1, -10928
Numeric / Double | fractions & decimals from -Inf to +Inf | 1.3, .293764, -.1239217, `Inf`, `-Inf`
Character / String | quoted strings of letters, numbers, and allowed symbols| "1", "one", "o_n_e", "o-n-e", "o.n.e"
Logical / Boolean | logical constants of True or False | `TRUE`, `FALSE`, `T`, `F`
factor | ordered, labelled variable | variable for year in college labelled "Freshman", "Sophomore", etc.

---
# Types of data 

+ There are a few special types worth knowing about too:

Type | Definition |Example
-----|------------|-------
NA   | Missing value; technically represented as different types but displayed as `NA` | `NA`, `NA_character_`, `NA_integer_`
NaN  | Not a Number | 0/0
+Inf | Positive infinity | `Inf`
-Inf | Negative infinity | `-Inf`
NULL | The `NULL` object; an object that exists but is completely empty | `NULL`

---
# Types of data 

+ You can use `typeof()` to find out the type of a value or object:

```{r}
typeof(1)
typeof(TRUE)
typeof(1L)
typeof("one")
```

---
# Types of data 

```{r}
typeof(NA)
typeof(NA_character_)
typeof(NULL)
typeof(Inf)
```

---
class: inverse, center, middle
# Data structures 

---
# Vectors 

+ Often, we’re not working with individual values, but with multiple related values or a **vector** of values.

--
***

+ We can create a vector of ordered numbers using `starting_number`:`ending_number`. For example, we could make `x` a vector with the numbers between 1 and 5.

```{r}
x <- 1:5
x
```

--
***
+ Let's look at the Environment pane in RStudio... `r icon::fa("cloud")` 

Since `x` is a vector, it tells us what type of vector it is and it's length in addition to its contents (which can be abbreviated if the object is larger).

---
# Vectors

We can create a vector of any numbers we want using the `c()` function. You do this by putting numbers seperated by a comma (`,`) within the parentheses.

```{r}
x <- c(2, 8.5, 1, 9)
x
```


--
***

We can also create a vector of numbers `seq()`. `seq()` is a function that creates a sequence of numbers. To learn how any R function works, you can access the help documentation by typing `?+function_name`. 

Let's take a look at how `seq()` works... `r icon::fa("cloud")` 

--
***

+ What happens if we run `seq()` with no arguments?
