---
title: "Your Turn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### RUN THIS CODE CHUNK FIRST TO LOAD NECESSARY PACKAGES ####

```{r}
library(tidyverse)
library(palmerpenguins)
library(rio)
library(here)
```


# Your Turn 1 

1. Run the code chunk provided to calculate the mean of `flipper_length_mm`.

```{r}
# Q1. 

mean(penguins$flipper_length_mm, na.rm = TRUE)
```

2. Take a glimpse at the data using `glimpse()` or `str()` to get a sense of the variables. You can also `View()` the data. 

```{r}
# Q2. 

```


3. Re-write the code above using the pipe operator, `%>%`. Check that the answer you get matches the original code you ran above. 

```{r}
# Q3.

```



# Your Turn 2

1. Create a scatter plot to visualize the relationship between `flipper_length_mm` and `bill_length_mm`. 

```{r}
# Q1.

penguins %>% 
  ggplot() + 
  ___(aes(x = ___, y = ___))
```


2. Build on your plot above by adding an aesthetic to visualize the effect of `species`. Choose any aesthetic you’d like or play around with a few. What do they do? How might you use more than one aesthetic? 

Options for aesthetics include `color`, `shape`, `size`, and `alpha` (transparency, 0-1 scale). 

```{r}
# Q2. 

```



# Your Turn 3

1. Import the dataset `pragmatic_scales_data.csv`, which is saved inside the `data` folder. 

```{r}
# Q1. 
ps_data <- rio::import(here::here("___"))
```


2. Take a glimpse at the data using `glimpse()` or `str()` to get a sense of the variables. You can also `View()` the data. 

```{r}
# Q2. 

```


3. Fill in the blanks in the code to re-create the plot below. *Note*: This plot uses a geom we haven't seen yet called `geom_bar()`, which I've filled in for you. 


```{r}
# Q3.

ps_data %>% 
  ggplot(aes(x = ___, y = ___, fill = ___)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~___)
```



