---
title: "Your Turn"
output: html_document
---

# Your Turn 1 

1. Create an object called `x` that is assigned the number 8. 

```{r}
# Q1.

```


2. Create an object called `y` that is a sequence of numbers from 2 to 16, by 2. (Replace the `___` with your code.)

```{r}
#Q2. 

y <- seq(from = ___, to = ___, by = ___)
```


3. Add `x` and `y`. What happens? 

```{r}
# Q3.


```


# Your Turn 2

1. Create an object called `a` that is just the letter "a" and an object `x` that is assigned the number 8. Add `a` to `x`. What happens?

```{r}
# Q1.

```


2. Create a vector called `b` that is just the number 8 in quotes. Add `b` to `x` (from above). What happens?

```{r}
# Q2.

```


3. Find some way to add `b` to `x`. (*Hint*: Don't forget about coercion.)

```{r}
# Q3. 

```


# Your Turn 3

1. Create a vector called `named` that includes the numbers 1 to 5. Name the values "a", "b", "c", "d", and "e" (in order). 

```{r}
# Q1.

named <- c(___)
```

2. Print the first element using numerical indexing and the last element using name indexing.

```{r}
# Q2.

```


3. Change the  third element of `named` to the value 21 and then show your results.

```{r}
# Q3. 

```


# Your Turn 4


1. Create a list like mine that is made up of `year`, `name`, `enrollment`, `fave_data`, but corresponds to you (year in undergrad, year in grad school, years since PhD, etc.). Make sure you enter two types of favorite data (bc who could choose?!). 

```{r}
# Q1. # name your list as your first name

___ <- list(___)
```


2. Index your list to print only your name.

```{r}
# Q2. 

```



# Your Turn 5

1. Make a data frame, called `df_2`, that has 3 columns as shown below. After you create it, check the structure.

    `c1` = c(1, 2, 3) <br>
    `c2` = c(2, 4, 6) <br>
    `c3` = c("a", "b", "c")

```{r}
# Q1. 

df_2 <- data.frame(___)


# check structure
___(df_2)
```


2. Add a fourth column, `c4`, which is the first and second columns multiplied together.

```{r}
# Q2. 

df_2$c4 <- ___
```


3. Try to add the first and second rows together. What happens? Why?

```{r}
# Q3. 

___ + ___
```

